---
title: "Syllabus for HIS 202H"
subtitle: Graduate seminar in c20 US history, Fall 2023
author: 
    - name: Eric Rauchway
      email: earauchway@ucdavis.edu
      affiliations:
          name: Department of History, University of California, Davis
date: last-modified
date-format: long
---

---
nocite: |
    [@krautThreatDissentHistory2020]
    [@mcgirrWarAlcoholProhibition2016]
    [@sweetHistoryHistory2022]
    [@rauchwayNewDealWas2019]
    [@morganSwingTimeNew2022]
    [@leuchtenburgWhenPeopleSpoke1999]
    [@daviesNewDeal19402015]
    [@williamsGreatDepressionNew2018]
    [@hannsgenDidNewDeal2010]
    [@hausmanRecoveryGreatDepression2019]
    [@grantGreatMigrationDemocratic2020]
    [@thurstonBoundariesHomeownershipCredit2018]
    [@wilsonDestructiveCreationAmerican2016]
    [@guglielmoMartialFreedomMovement2018]
    [@katznelsonLimitingLiberalismSouthern1993]
    [@gallicchioUnconditionalJapaneseSurrender2020]
    [@asadaShockAtomicBomb1998]
    [@hasegawaTsuyoshiHasegawaVs2006]
    [@bernsteinAtomicBombingsReconsidered1995]
    [@johnsonLavenderScareCold2004]
    [@schreckerMcCarthyismPoliticalRepression2004]
    [@olmstedConspiracyDenseDubious2018]
    [@johnsonReformingJimCrow2010]
    [@cha-juaLongMovementVampire2007]
    [@schicklerNewDealLiberalism2013]
    [@mackenzieLiberalHourWashington2008]
    [@tuckIntroductionReconsidering1970s2008]
    [@daviesBiggovernmentConservatismConservatives2008]
    [@tuckWeAreTaking2008]
    [@hallProtestMovements1970s2008]
    [@zeitzRejectingCenterRadical2008]
    [@jacobsCommentSwingingToo2008]
    [@schulmanCommentEmpireStrikes2008]
    [@belewBringWarHome2018]
    [@zelizerReflectionsRethinkingHistory2010]
    [@perlsteinCorrections2017]
    [@leeAmericaAmericansHistory2019]
    [@serwerCrueltyPoint2018]
---

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
read_csv(file = "reading_calendar.csv") -> rc
rc |>
    mutate(new_date = format(Date, "%B %e")) |>
    select(c("Date" = "new_date", Assignment)) -> rc_f
```

# Introduction

This course provides an introduction to some basic themes and literature of twentieth-century US history. Course aims include the standard graduate seminar goals of developing participants' ability to analyze and criticize arguments, including especially an understanding of sources and methods; also the more practical goal of learning how to present such analysis and critique to best effect. You should finish the seminar with a reasonably good foundation for further reading for your comprehensive examinations, and also for constructing a survey course in twentieth-century US history.[Please note the date of the version of the syllabus you are reading; if it is before the start of the term it is quite likely there is a more recent version available.]{.aside}

This seminar meets weekly on Monday afternoon, 3:10--6:00 p.m., in Social Sciences room 4217.

# Course calendar

You should ensure you have access to the required reading (please see the list below) and that you have read it thoroughly prior to the class meeting for which it is assigned in this calendar. You should come to class prepared to discuss the authors' arguments, sources, and methods of analysis and presentation, and in seminar you should pose questions and propose answers and otherwise participate actively. You should complete work as assigned. [If you do not already have a short shelf of texts on how to write, and specifically how to write history, you might begin to accumulate one before this course starts. Style guides include the old classics, like Strunk & White, *The Elements of Style,* as well as *Dreyer's English,* a recently published instant classic. On the conduct of history you might begin with Bloch, *The Historian's Craft.*]{.aside} 

```{r echo = FALSE, warning = FALSE, message = FALSE}
#| tbl-colwidths: [20, 80]
rc_f |>
    kable(format = "pipe") |>
    kable_styling(full_width = TRUE)
```


[Links appear in this list for readings that can be found only online. All readings have been registered with the campus bookstore and with library reserves as of the end of July. Beyond that, it is up to you---and this is part of the practical training of the course---to acquire the readings in a timely fashion. You will find you can get all of them using resources available as of this writing.]{.aside}
